Deciding to Disclose

### 2015-09-16 Introduction.tex
equilibrium

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change. This is clearly desirable where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement.
Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem. In addition, rules are agnostic as to where the source of information, suggesting room for multi-stage processes.  As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions. This is also indicative of the broader benefits to \ac{ABM} as an approach. Embedding these abstract rules in a simulated environment allows for mechanics which cannot be readily explored using purely analytic, or predictive approaches, for example, the social learning dynamic of the disclosure game model.

@@

Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is process, and decision making. Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away yields a computationally tractable approach. Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.

>>>>

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. But equilibrium is the sine qua non of game theory, which is concerned with the stable outcome of an infinite contest of second guesses.
We wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point. Instead, we choose to focus instead on the behavioural processes driving a system in motion, a system out of equilibrium, to understand how these processes interact with the movement.
Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory. Dealing instead in the mechanics of decision making, and the calculus of choice, allows us to explore not only paths that arrive at the destinations we might consider in game theory, but also avenues not accessible where we constrain ourselves to a sometimes implausible degree of rationality.

This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem. In addition, rules are agnostic as to the source of information, suggesting room for multi-stage processes - for example, a more game theoretic, model of the opponent's mind, type approach could act as an information source for a decision rule.  As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions. This is also indicative of the broader benefits to \ac{ABM} as an approach. Embedding these abstract rules in a simulated environment allows for mechanics which cannot be readily explored using purely analytic, or predictive approaches, for example, the social learning dynamic of the disclosure game model.

@@

Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is process, and decision making. Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away, yields a computationally tractable approach. Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.
